A publishing infrastructure for AI-assisted academic authoring

### 2023-12-26 latex/manuscript.tex
latex/latexdiff bug: remove section hypertarget command

\hypertarget{authors}{%
\subsection{Authors}\label{authors}}

@@

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

@@

\hypertarget{introduction}{%
\subsection{Introduction and background}\label{introduction}}

@@

\hypertarget{objective}{%
\subsection{Objective}\label{objective}}

@@

\hypertarget{materials-and-methods}{%
\subsection{Materials and Methods}\label{materials-and-methods}}

@@

\hypertarget{overview-of-the-manubot-ai-editor}{%
\subsubsection{Overview of the Manubot AI Editor}\label{overview-of-the-manubot-ai-editor}}

@@

\hypertarget{implementation-details}{%
\subsubsection{Implementation details}\label{implementation-details}}

@@

\hypertarget{properties-of-language-models}{%
\subsubsection{Properties of language models}\label{properties-of-language-models}}

@@

\hypertarget{installation-and-use}{%
\subsubsection{Installation and use}\label{installation-and-use}}

@@

\hypertarget{sec:results}{%
\subsection{Results}\label{sec:results}}

\hypertarget{evaluation-setup}{%
\subsubsection{Evaluation setup}\label{evaluation-setup}}

@@

\hypertarget{language-models}{%
\paragraph{Language models}\label{language-models}}

@@

\hypertarget{manuscripts}{%
\paragraph{Manuscripts}\label{manuscripts}}

@@

\hypertarget{evaluation-using-human-assessments}{%
\paragraph{Evaluation using human assessments}\label{evaluation-using-human-assessments}}

@@

\hypertarget{prompt-engineering}{%
\paragraph{Prompt engineering}\label{prompt-engineering}}

@@

\hypertarget{general-assessment-of-language-models}{%
\subsubsection{General assessment of language models}\label{general-assessment-of-language-models}}

@@

\hypertarget{revision-of-different-sections}{%
\subsubsection{Revision of different sections}\label{revision-of-different-sections}}

@@

\hypertarget{abstract-1}{%
\paragraph{Abstract}\label{abstract-1}}

@@

\hypertarget{introduction-1}{%
\paragraph{Introduction}\label{introduction-1}}

@@

\hypertarget{results}{%
\paragraph{Results}\label{results}}

@@

\hypertarget{discussion}{%
\paragraph{Discussion}\label{discussion}}

@@

\hypertarget{methods}{%
\paragraph{Methods}\label{methods}}

@@

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

@@

\hypertarget{conclusions}{%
\subsection{Conclusions}\label{conclusions}}

@@

\hypertarget{funding-statement}{%
\subsection{Funding statement}\label{funding-statement}}

@@

\hypertarget{competing-interests-statement}{%
\subsection{Competing interests statement}\label{competing-interests-statement}}

@@

\hypertarget{data-availability-statement}{%
\subsection{Data availability statement}\label{data-availability-statement}}

@@

\hypertarget{contributorship-statement}{%
\subsection{Contributorship statement}\label{contributorship-statement}}

@@

\hypertarget{references}{%
\subsection{References}\label{references}}

>>>>

\subsection{Authors}

@@

\subsection{Abstract}

@@

\subsection{Introduction and background}

@@

\subsection{Objective}

@@

\subsection{Materials and Methods}

@@

\subsubsection{Overview of the Manubot AI Editor}

@@

\subsubsection{Implementation details}

@@

\subsubsection{Properties of language models}

@@

\subsubsection{Installation and use}

@@

\subsection{Results}

\subsubsection{Evaluation setup}

@@

\paragraph{Language models}

@@

\paragraph{Manuscripts}

@@

\paragraph{Evaluation using human assessments}

@@

\paragraph{Prompt engineering}

@@

\subsubsection{General assessment of language models}

@@

\subsubsection{Revision of different sections}

@@

\paragraph{Abstract}

@@

\paragraph{Introduction}

@@

\paragraph{Results}

@@

\paragraph{Discussion}

@@

\paragraph{Methods}

@@

\subsection{Discussion}

@@

\subsection{Conclusions}

@@

\subsection{Funding statement}

@@

\subsection{Competing interests statement}

@@

\subsection{Data availability statement}

@@

\subsection{Contributorship statement}

@@

\subsection{References}
